Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
Include updates to the introduction

The vast majority of SNe Ia are observed 
to be powered purely by the radioactive decay of $^{56}$Ni. 
While the detection of SN shock cooling or ejecta interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can fundamentally alter the appearance of the SN shortly after explosion. SNe Ia experience a dark phase after
the SN shock breakout but before radioactive energy  
diffuses into the photosphere \citep{2014ApJ...784...85P}. The 
duration of this dark phase is set by how the newly synthesized 
$^{56}$Ni is mixed and deposited into different layers of the ejecta. In the case of strong mixing, the dark phase is short, or 
non-existent, as $\gamma$-rays from the radioactive $^{56}$Ni diffuse to the photosphere rapidly. This also leads to blue optical colors and a rapid initial rise in the observed light curve. If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark phase can last for several days. The early evolution of such SNe results in redder colors and a more moderate rise in luminosity \citep{2016ApJ...826...96P}. Thus, the early light curves of even non-exotic Type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.\footnote{\citet{2015A&A...574A..60T} found that a significant dark phase is not prevalent for a sample of Type Ib/c SNe.}

\citet{2017MNRAS.472.2787N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging. \citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2\,d using common methods in the literature. While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}. Reconciling these issues requires both a larger sample of early SNe Ia observations and more detailed models that produce synthetic light curves and spectra.

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.49\textwidth]{CarbonFeature.pdf}
  \caption{Evolution of the \ion{C}{2} features observed in the 
  early spectra of \abc. The raw spectra are shown in orange, while 
  the solid blue lines show the best-fit models including Gaussian 
  components for each line and a linear component for the continuum 
  (see text for further details). The dark grey vertical lines show 
  the measured line centers, indicating the decline in the 
  photosphere velocity in the $\sim$7~d after explosion (note that 
  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d 
  spectrum). The phase of each spectrum relative to 
  $T_{B,\mathrm{max}}$ is labeled.
  }
  \label{fig:carbon}
\end{figure}

@@

\section{Discussion: \textbf{Modeling the Early Evolution of \abc}}
\label{sec:lc_energy}

@@

\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the observations as the N100 model features a faster rise and higher luminosity than what is observed. We explore delayed detonation models in further detail below.
}

>>>>

The vast majority of SNe Ia are observed to be powered purely by the
radioactive decay of $^{56}$Ni. While the detection of SN shock cooling or
ejecta interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can
fundamentally alter the appearance of the SN shortly after explosion
\textbf{(e.g.,
\citealt{2014MNRAS.441..532D,2016ApJ...826...96P,2017MNRAS.466.3784S,2017MNRAS.472.2787N})}.

SNe Ia experience a dark phase after the SN shock breakout but before
radioactive energy diffuses into the photosphere \citep{2014ApJ...784...85P}.
The duration of this dark phase is set by how the newly synthesized $^{56}$Ni
is mixed and deposited into different layers of the ejecta. In the case of
strong mixing, the dark phase is short, or non-existent, as $\gamma$-rays from
the radioactive $^{56}$Ni diffuse to the photosphere rapidly. This also leads
to blue optical colors and a rapid initial rise in the observed light curve.
\textbf{Even with vigorous mixing it is difficult at very early times, $<
1$\,d after explosion, to explain very large luminosities or blue colors,
because the $^{56}$Ni has not had sufficient time to radioactively decay to
$^{56}$Co.} If the mixing is weak and the $^{56}$Ni is confined to the
innermost layers of the ejecta, the dark phase can last for several days. The
early evolution of such SNe results in redder colors and a more moderate rise
in luminosity \citep{2014MNRAS.441..532D,2016ApJ...826...96P}. Thus, the early
light curves of even non-exotic Type Ia SNe convey information about their
progenitor systems by constraining the distribution of synthesized $^{56}$Ni,
which in turn constrains the explosion mechanism.

% \footnote{\citet{2015A&A...574A..60T} found that a significant dark
% phase is not prevalent for a sample of Type Ib/c SNe.}

\citet{2017MNRAS.472.2787N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging. \citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as \textbf{much} as $\sim$2\,d using common methods in the literature. While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}. Reconciling these issues requires both a larger sample of early SNe Ia observations and more detailed models that produce synthetic light curves and spectra.

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.49\textwidth]{CarbonFeature.pdf}
  \caption{
  Evolution of the \ion{C}{2} features observed in the early spectra of \abc.
  The raw spectra are shown in orange, while the solid blue lines show the
  best-fit models including Gaussian components for each line and a linear
  component for the continuum (see text for further details). The dark grey
  vertical lines show the measured line centers, indicating the decline in the
  photosphere velocity in the $\sim$7~d after explosion (note that
  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d spectrum). The
  phase of each spectrum relative to $T_{B,\mathrm{max}}$ is labeled.
  }
  \label{fig:carbon}
\end{figure}

@@

\section{\textbf{Modeling the Early Evolution of \abc}} \label{sec:lc_energy}

@@

\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the
observations as the N100 model features a faster rise and higher luminosity
than what is observed. We explore delayed detonation models in further detail
below.}
